Title of the Master Thesis

### 2015-10-01 Master Thesis/synopsis.tex
Add labels

\begin{proposition}
Let $K_0/K$ be an algebraic extension.
\begin{enumerate}[(i)]
\item Suppose there exists a prime number $\ell$ with $\ell^\infty\nmid[K_0:K]$ and such that for every algebraic extension $L/K_0$ we have: 
\[ \mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z}) = \begin{cases}
\mathbb{Z}/\ell\mathbb{Z}, & \ell^\infty\nmid [L:K_0]\\
0, & \text{otherwise}
\end{cases} \]
Then there exists a unique henselian $w\in|\operatorname{Spv}(K)|$.
\item Assume that the hypothesis of (i) is satisfied for two different prime numbers. Then $w$ is defectless.
\end{enumerate}
\end{proposition}

@@

\begin{lemma}
Let $w\in\operatorname{Spv}_\text{d}^{(2)}(K)$ and let $E=K_w$ be a henselization of $w$. Then $E'$ is a henselization of $K'$ with respect to a unique $w'\in\operatorname{Spv}_\text{d}^{(2)}(K')$. The map $w\mapsto w'$ does not depend on the choice of the henselization.
\end{lemma}

\begin{lemma}
$\sigma$ induces a bijection $\sigma:\operatorname{Spv}_\text{d}^{(1)}(K)\to\operatorname{Spv}_\text{d}^{(1)}(K')$. If $E=K_v\subset\overline{K}$ is a henselization of $K$ with respect to $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$ then $E'$ is a henselization of $K'$ with respect to $v'=\sigma(v)$. Furthermore, if $E^{\text{t}}$ and $E'^{\text{t}}$ denotes the inertial fields of $E$ and $E'$ respectively, then $\sigma$ induces an isomorphism:
\[ G_{k(v)}\cong\operatorname{Gal}(E^\text{t}/E)\to\operatorname{Gal}(E'^{\text{t}}/E')\cong G_{k(v')} \]
which is induced by a unique isomorphism $\varphi_v^\text{s}:k(v')^\text{s}\to k(v)^\text{s}$. In particular $\varphi_v=\varphi_v^\text{s}|_{k(v')}:k(v')\to k(v)$ is an isomorphism.
\end{lemma}

>>>>

\begin{proposition}\label{2.6}
Let $K_0/K$ be an algebraic extension.
\begin{enumerate}[(i)]
\item Suppose there exists a prime number $\ell$ with $\ell^\infty\nmid[K_0:K]$ and such that for every algebraic extension $L/K_0$ we have: 
\[ \mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z}) = \begin{cases}
\mathbb{Z}/\ell\mathbb{Z}, & \ell^\infty\nmid [L:K_0]\\
0, & \text{otherwise}
\end{cases} \]
Then there exists a unique henselian $w\in|\operatorname{Spv}(K)|$.
\item Assume that the hypothesis of (i) is satisfied for two different prime numbers. Then $w$ is defectless.
\end{enumerate}
\end{proposition}

@@

\begin{lemma}\label{3.1}
Let $w\in\operatorname{Spv}_\text{d}^{(2)}(K)$ and let $E=K_w$ be a henselization of $w$. Then $E'$ is a henselization of $K'$ with respect to a unique $w'\in\operatorname{Spv}_\text{d}^{(2)}(K')$. The map $w\mapsto w'$ does not depend on the choice of the henselization.
\end{lemma}

\begin{lemma}\label{3.2}
$\sigma$ induces a bijection $\sigma:\operatorname{Spv}_\text{d}^{(1)}(K)\to\operatorname{Spv}_\text{d}^{(1)}(K')$. If $E=K_v\subset\overline{K}$ is a henselization of $K$ with respect to $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$ then $E'$ is a henselization of $K'$ with respect to $v'=\sigma(v)$. Furthermore, if $E^{\text{t}}$ and $E'^{\text{t}}$ denotes the inertial fields of $E$ and $E'$ respectively, then $\sigma$ induces an isomorphism:
\[ G_{k(v)}\cong\operatorname{Gal}(E^\text{t}/E)\to\operatorname{Gal}(E'^{\text{t}}/E')\cong G_{k(v')} \]
which is induced by a unique isomorphism $\varphi_v^\text{s}:k(v')^\text{s}\to k(v)^\text{s}$. In particular $\varphi_v=\varphi_v^\text{s}|_{k(v')}:k(v')\to k(v)$ is an isomorphism.
\end{lemma}
